Prefetching SPARQL query cacher

### 2016-05-26 dissertation/cache-proxy.tex
explain TPF vs LDF

>>>>

Finally note that in this text, the term Triple Pattern Fragment is
understood as a specialisation of Linked Data Fragments, in which a
Triple Pattern Fragment server must be able to answer any triple
pattern, whereas for a Linked Data Fragments server, this is not
required. However, there is no difference in the current
implementation, so in practice, the terms could be used
interchangeably.
